### 2016-05-17 syntax.tex
cheers

\paragraph{Basic Bloom filter syntax.}
Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(H,\mathsc{Rep},\mathsc{Qry})$.

The hash family $H = \{h_i : U \rightarrow [m]  | i in [k]\}$ is  set of~$k$ hash functions.

The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.  The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.  Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.

@@

\jknote{Why not simply include the description of the hash function(s) as part of the size of the representation? I.e., Have $B_1$, $B_2$ exactly as in the paper, but explicitly count the bits needed to represent the hash functions as part of the representation output by $B_1$.}
\tsnote{See my comments above.}
\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets$ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}

@@

Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.

A “Bloom filter with operations” is a four-tuple  $B=(H,\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.

As before, the hash family $H = \{h_i : U \rightarrow [m]  | i in [k] \}$ is  set of~$k$ hash functions.

@@

The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.

>>>>

\paragraph{Basic Bloom filter syntax.}
Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(\mathcal{H},\mathsc{Rep},\mathsc{Qry})$.   The hash family $\mathcal{H} = \{h_i : U \rightarrow [m]  \,|\,  i \in [k]\}$ is  set of~$k$ hash functions.

The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.  The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$\mathcal{H}$.  Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.

@@

\jknote{Why not simply include the description of the hash function(s) as part of the size of the representation? I.e., Have $B_1$, $B_2$ exactly as in the paper, but explicitly count the bits needed to represent the hash functions as part of the representation output by $B_1$.}
\tsnote{See my comments above.}
\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets $ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}

@@

Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.  
A “Bloom filter with operations” is a four-tuple  $B=(\mathcal{H},\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.  
As before, the hash family $\mathcal{H} = \{h_i : U \rightarrow [m]  \,|\,  i \in [k] \}$ is  set of~$k$ hash functions.

@@

The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$\mathcal{H}$.
